Viscous Transport in Eroding Porous Media

### 2019-10-03 docs/transport/erosion_transport.tex
NM

The transport is characterized in terms of tortuosity and anomalous
dispersion. The local tortuosity agrees qualitatively with
other works~\cite{mat-kha-koz2008}. However, the tortuosity of the
eroded geometries can not be completely described in terms of the
porosity. In particular, we observe that for certain porous media, the
tortuosity can increase when the porosity increases under erosion. We
also observe super-dispersive spreading, and the rate of dispersion
significantly depends not only on the porosity, but also the number of
eroding bodies.

@@

As a long term goal, we would like to include the effect of inertia and
other transport models. Including inertia requires an integral equation
formulation for the Navier-Stokes equations, and one approach has
recently been developed~\cite{kli-ask-kro2019}. Regarding other
transport models, this would involve a diffusive term to consider the
transport of heat or a contaminant. Forming high-fidelity simulations of
such an advection-diffusion equation can be accomplished by using time
splitting methods and recent work on heat solvers in complex
geometries~\cite{fry-kro-tor2019}.

>>>>

The transport is characterized in terms of tortuosity and anomalous
dispersion. The local tortuosity agrees qualitatively with
other works~\cite{mat-kha-koz2008}. However, the tortuosity of the
eroded geometries \nick{\st{can not} cannot} be completely described in terms of the
porosity. In particular, we observe that for certain porous media, the
tortuosity can increase when the porosity increases under erosion. We
also observe super-dispersive spreading, and the rate of dispersion
significantly depends not only on the porosity, but also the number of
eroding bodies.

@@

As a long term goal, we would like to include the effect of inertia and
other transport models. Including inertia requires an integral equation
formulation of the Navier-Stokes equations, \nick{which is an active area of research with a few promising algorithms recently proposed}~\cite{gray2019boundary, kli-ask-kro2019}. 
\todo[inline]{Okay with you if I include my work with Lenny here? After all, the end goal of it is to solve Navier-Stokes with boundary integrals :)}
Regarding other transport models, this would involve a diffusive term to consider the
transport of heat or a contaminant. Forming high-fidelity simulations of
such an advection-diffusion equation can be accomplished by using time
splitting methods and recent work on heat solvers in complex
geometries~\cite{fry-kro-tor2019}.
